### 2021-02-11 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
Edits to SH chapter

\chapter{Spherical harmonics as orthogonal polynomials in three variables}

@@

\begin{lemma}
	For $l \in \No$, $m \in \Z$ s.t. $0 \le |m| \le l$, the spherical harmonics satisfy the relationships:
\bseqnnumber{
	x\,\Ylm(x,y,z) &= \alpha_{l,m,1} Y^{m-1}_{l-1}(x,y,z) +  \alpha_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \nonumber \\
		     & \quad \quad \quad + \alpha_{l,m,3} Y^{m-1}_{l+1}(x,y,z) + \alpha_{l,m,4} Y^{m+1}_{l+1}(x,y,z), \label{eqn:shrecx} \\
	y\,\Ylm(x,y,z) &= \beta_{l,m,1} Y^{m-1}_{l-1}(x,y,z) +  \beta_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \nonumber \\
		     & \quad \quad \quad + \beta_{l,m,3} Y^{m-1}_{l+1}(x,y,z) + \beta_{l,m,4} Y^{m+1}_{l+1}(x,y,z), \label{eqn:shrecy} \\
	z\,\Ylm(x,y,z) &= \gamma_{l,m,1} Y^{m}_{l-1}(x,y,z) + \gamma_{l,m,2} Y^{m}_{l+1}(x,y,z), \label{eqn:shrecz}
}
where
\bseqn{
	\alpha_{l,m,1} &:= 
		\begin{cases}
			\frac{\alphalm}{2\alpha^{m-1}_{l-1}} \tilde \alpha_{l,m,1} \quad \text{if } m>0 \\
			\frac{\alphalm}{2\alpha^{m-1}_{l-1}} \tilde \alpha_{l,|m|,2} \quad \text{if } m\le0 , \, l - |m| \ge 2 \\
			\quad \quad 0 \quad \quad \quad \quad \text{otherwise} 
		\end{cases} \\ 
	\alpha_{l,m,2} &:= 
		\begin{cases}
			\frac{\alphalm}{2\alpha^{m+1}_{l-1}} \tilde \alpha_{l,m,2} \quad \text{if } m\ge0, \, l - |m| \ge 2 \\
			\frac{\alphalm}{2\alpha^{m+1}_{l-1}} \tilde \alpha_{l,|m|,1} \quad \text{if } m<0 \\
			\quad \quad 0 \quad \quad \quad \quad \text{otherwise} 
		\end{cases} \\
	\alpha_{l,m,3} &:= 
		\begin{cases}
			\frac{\alphalm}{2\alpha^{m-1}_{l+1}} \tilde \alpha_{l,m,3} \quad \text{if } m>0 \\
			\frac{\alphalm}{2\alpha^{m-1}_{l+1}} \tilde \alpha_{l,|m|,4} \quad \text{if } m\le0 
		\end{cases} \\
	\alpha_{l,m,4} &:=
		\begin{cases}
			\frac{\alphalm}{2\alpha^{m+1}_{l+1}} \tilde \alpha_{l,m,4} \quad \text{if } m\ge0 \\
			\frac{\alphalm}{2\alpha^{m+1}_{l+1}} \tilde \alpha_{l,|m|,3} \quad \text{if } m<0 
		\end{cases} \\
	\beta_{l,m,j} &:= (-1)^{j+1} \: i \: \alpha_{l,m,j}, \quad j = 1,2,3,4 \\
	\gamma_{l,m,1} &:= \frac{\clm}{c^{m}_{l-1}} \: \tilde \gamma_{l,m,1} \\
	\gamma_{l,m,2} &:= \frac{\clm}{c^{m}_{l+1}} \: \tilde \gamma_{l,m,2}.
}
and
\bseqn{
	\tilde \alpha_{l,m,1} &:= \frac{2l}{2l+1} \\
	\tilde \alpha_{l,m,2} &:= 
		\begin{cases}
			- \frac{l}{2(2l+1)} \quad \text{if } l - m \ge 2 \\
			\quad \quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \alpha_{l,m,3} &:= - \frac{2(l-m+2)(l-m+1)}{(2l+1)(l+1)} \\
	\tilde \alpha_{l,m,4} &:= \frac{(l+m+2)(l+m+1)}{2(2l+1)(l+1)} \\
	\tilde \gamma_{l,m,1} &:= \begin{cases}
			\frac{l}{2l+1} \quad \text{if } l - m \ge 1 \\
			\quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \gamma_{l,m,2} &:= \frac{(l-m+1)(l+m+1)}{(2l+1)(l+1)}.
}
\end{lemma}

@@

\subsection{Variable coefficients as operators}

@@

%%%
\section{Tangent space -- vector spherical harmonics as orthogonal vectors in three variables}

@@

\subsection{Vector spherical harmonics as a vector-weighted sum of scalar spherical harmonics} %{Spin-1 tensor spherical harmonics}

The vector spherical harmonics in \bsrefeqn{eqn:VSHs} can be expressed in terms of \textit{spin-1 tensor spherical harmonics}, which in turn can each be expressed as a vector-weighted sum of spherical harmonics \cite{khersonskii1988quantum}.

We start by defining what we mean by a spin-1 tensor spherical harmonic. In general, the tensor spherical harmonic is given by, for $2l, \, j, \, 2s \in \No$,
\bseqn{
	\curlyy^{j,s}_{l,m}(x,y,z) = \sum_{m_s=-s}^s \langle j \quad m-m_s \; ; \; s \quad m_s \; | \; l \quad m \rangle \, Y^{m-m_s}_j (x,y,z) \, \vec{\chi}_{s, m_s},
}
where $\vec{\chi}_{s, m_s}$ are the simultaneous eigenstates of the spin operators $\bold{S}^2$ and $S_z$, and where $\langle j \quad m-m_s \; ; \; s \quad m_s \; | \; l \quad m \rangle$ is a Clebsch-Gordan coefficient \cite{} \bstodo{cite C-G coeffs}. We note that a property of the Clebsch--Gordan coefficients means that they vanish unless $|j - s| \le l \le j + s$. We further note that there are simple calculable expressions for the Clebsch--Gordan coefficients when the spin $s=1$.

To simplify the notation, for spin $s=1$, we define
\bseqnnumber{
	\cgcoeff^{L, m_s}_{l, m} := \, \langle L \quad m-m_s \; ; \; 1 \quad m_s \; | \; l \quad m \rangle. \label{eqn:cgcoeffdef}
}
Thus we have that the three spin-1 tensor spherical harmonics are given by
\bseqn{
	\curlyy^{l \pm1,s}_{l,m}(x,y,z) &= \sum_{m_s=-1}^1 \cgcoeff^{l\pm1, m_s}_{l, m} \, Y^{m-m_s}_{l \pm 1} (x,y,z) \, \chivec, \\
	\curlyy^{l,s}_{l,m}(x,y,z) &= \sum_{m_s=-1}^1 \cgcoeff^{l, m_s}_{l, m} \, Y^{m-m_s}_l (x,y,z) \, \chivec.
}

Here, the vectors $\chivec$ are the orthonormal eigenvectors of the matrix
\bseqn{
	S_3 = \begin{pmatrix} 0 & -i & 0 \\ i & 0 & 0 \\ 0 & 0 & 0 \end{pmatrix},
}
and so are given as
\bseqn{
	\vec{\chi}_{1, \pm 1} = \frac{1}{\sqrt{2}} \begin{pmatrix} \mp 1 \\ -i \\ 0 \end{pmatrix}, \quad \vec{\chi}_{1,0} = \begin{pmatrix} 0 \\ 0 \\ 1 \end{pmatrix}.
}
Then, for any $l \in \No$, $m \in \Z$ s.t. $0 \le |m| \le l$ we have that
\bseqnnumber{
	\gradYlm &= \mu_{l,-1} \, \curlyy^{l-1,1}_{l,m} + \mu_{l,1} \curlyy^{l+1,1}_{l,m}, \quad \gradpYlm = \mu_{l,0} \, \curlyy^{l,1}_{l,m},\label{eqn:VSHsalt}
}
where \bstodoinline{get better reference than that Winter 2017 physics document}
\bseqnnumber{
	\mu_{l,-1} &:= (l+1) \, \Big(\frac{l}{2l+1}\Big)^\half, \quad
	\mu_{l,0} := i \, \big(l(l+1)\big)^\half, \quad 
	\mu_{l,1} := l \, \Big(\frac{l+1}{2l+1}\Big)^\half. \label{eqn:spintensorvshcoeffsdef}
}

\subsection{Jacobi matrices}

We start as before for the scalar case by finding $x \,\gradYlm (x,y,z)$, $x \,\gradpYlm (x,y,z)$ etc. in terms of $\gradY^{m'}_{l'} (x,y,z)$, $\gradpY^{m'}_{l'} (x,y,z)$. 
\begin{lemma}\label{lemma:VSHrecurrences}
	For $l \in \No$, $-l \le m \le l$ the vector spherical harmonics satisfy the relationships:
\bseqn{
	x \gradYlm &= A_{l,m,1} \gradY^{m-1}_{l-1} + A_{l,m,2} \gradY^{m+1}_{l-1} + A_{l,m,5} \gradY^{m-1}_{l+1} + A_{l,m,6} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + A_{l,m,3}^{*} \gradpY^{m-1}_{l} + A_{l,m,4}^{*} \gradpY^{m+1}_{l}, \\
	x \gradpYlm &= A_{l,m,1}^{*} \gradpY^{m-1}_{l-1} + A_{l,m,2}^{*} \gradpY^{m+1}_{l-1} + A_{l,m,5}^{*} \gradpY^{m-1}_{l+1} + A_{l,m,6}^{*} \gradpY^{m+1}_{l+1} \\
	& \quad \quad \quad + A_{l,m,3} \gradY^{m+1}_{l} + A_{l,m,4} \gradY^{m-1}_{l}, \\
	y \gradYlm &= B_{l,m,1} \gradY^{m-1}_{l-1} + B_{l,m,2} \gradY^{m+1}_{l-1} + B_{l,m,5} \gradY^{m-1}_{l+1} + B_{l,m,6} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + B_{l,m,3}^{*} \gradpY^{m-1}_{l} + B_{l,m,4}^{*} \gradpY^{m+1}_{l}, \\
	y \gradpYlm &= B_{l,m,1}^{*} \gradpY^{m-1}_{l-1} + B_{l,m,2}^{*} \gradpY^{m+1}_{l-1} + B_{l,m,5}^{*} \gradpY^{m-1}_{l+1} + B_{l,m,6}^{*} \gradpY^{m+1}_{l+1} \\
	& \quad \quad \quad + B_{l,m,3} \gradY^{m+1}_{l} + B_{l,m,4} \gradY^{m-1}_{l}, \\
	z \gradYlm &= \Gamma_{l,m,1} \gradY^{m}_{l-1} + \Gamma_{l,m,3} \gradY^{m}_{l+1} + \Gamma_{l,m,2}^* \gradpY^{m}_{l}, \\
	z \gradpYlm &= \Gamma_{l,m,1}^* \gradpY^{m}_{l-1} + \Gamma_{l,m,3}^* \gradpY^{m}_{l+1} + \Gamma_{l,m,2} \gradY^{m}_{l}
}
where $*$ denotes the complex conjugate, and where, for any valid $m_s$ value,
\bseqn{
	A_{l,m,1} &:= \frac{\mu_{l,-1}}{\mu_{l-1,-1}} \frac{\cgcoeff^{l-1,m_s}_{l,m}}{\cgcoeff^{l-2,m_s}_{l-1,m-1}} \alpha_{l-1,m-m_s,1}, \\
	A_{l,m,2} &:= \frac{\mu_{l,-1}}{\mu_{l-1,-1}} \frac{\cgcoeff^{l-1,m_s}_{l,m}}{\cgcoeff^{l-2,m_s}_{l-1,m+1}} \alpha_{l-1,m-m_s,2}, \\
	A_{l,m,3} &:= \frac{1}{\mu_{l,0} \, \cgcoeff^{l,m_s}_{l, m-1}} \, \Big[ \cgcoeff^{l-1,m_s}_{l,m} \, \mu_{l,-1} \, \alpha_{l-1,m-m_s,3} + \cgcoeff^{l+1,m_s}_{l,m} \, \mu_{l,1} \, \alpha_{l-1,m-m_s,1} \\
	& \quad \quad \quad \quad \quad \quad \quad - A_{l,m,5} \, \mu_{l+1,-1} \, \cgcoeff^{l,m_s}_{l+1,m-1} - A_{l,m,1} \, \mu_{l-1,1} \, \cgcoeff^{l,m_s}_{l-1,m-1} \Big], \\	
	A_{l,m,4} &:= \frac{1}{\mu_{l,0} \, \cgcoeff^{l,m_s}_{l, m+1}} \, \Big[ \cgcoeff^{l-1,m_s}_{l,m} \, \mu_{l,-1} \, \alpha_{l-1,m-m_s,4} + \cgcoeff^{l+1,m_s}_{l,m} \, \mu_{l,1} \, \alpha_{l-1,m-m_s,2} \\
	& \quad \quad \quad \quad \quad \quad \quad - A_{l,m,6} \, \mu_{l+1,-1} \, \cgcoeff^{l,m_s}_{l+1,m+1} - A_{l,m,2} \, \mu_{l-1,1} \, \cgcoeff^{l,m_s}_{l-1,m+1} \Big], \\
	A_{l,m,5} &:= \frac{\mu_{l,1}}{\mu_{l+1,1}} \frac{\cgcoeff^{l+1,m_s}_{l,m}}{\cgcoeff^{l+2,m_s}_{l+1,m-1}} \alpha_{l+1,m-m_s,3}, \\
	A_{l,m,6} &:= \frac{\mu_{l,1}}{\mu_{l+1,1}} \frac{\cgcoeff^{l+1,m_s}_{l,m}}{\cgcoeff^{l+2,m_s}_{l+1,m+1}} \alpha_{l+1,m-m_s,4}, \\
	B_{l,m,j} &:= i (-1)^{j+1} A_{l,m,j} \quad \text{for } j = 1,\dots,6, \\
	\Gamma_{l,m,1} &:= \frac{\mu_{l,-1}}{\mu_{l-1,-1}} \frac{\cgcoeff^{l-1,m_s}_{l,m}}{\cgcoeff^{l-2,m_s}_{l-1,m+1}} \gamma_{l-1,m-m_s,1}, \\
	\Gamma_{l,m,2} &:= \frac{1}{\mu_{l,0} \, \cgcoeff^{l,m_s}_{l, m}} \, \Big[ \cgcoeff^{l-1,m_s}_{l,m} \, \mu_{l,-1} \, \gamma_{l-1,m-m_s,2} + \cgcoeff^{l+1,m_s}_{l,m} \, \mu_{l,1} \, \gamma_{l+1,m-m_s,1} \\
	& \quad \quad \quad \quad \quad \quad \quad - \Gamma_{l,m,3} \, \mu_{l+1,-1} \, \cgcoeff^{l,m_s}_{l+1,m} - \Gamma_{l,m,1} \, \mu_{l-1,1} \, \cgcoeff^{l,m_s}_{l-1,1} \Big], \\
	\Gamma_{l,m,3} &:= \frac{\mu_{l,1}}{\mu_{l+1,1}} \frac{\cgcoeff^{l+1,m_s}_{l,m}}{\cgcoeff^{l+2,m_s}_{l+1,m+1}} \gamma_{l+1,m-m_s,2},
}
and where $\cgcoeff^{l,m_s}_{l',m'}$, $\mu_{l,k}$ are defined in \bsrefeqn{eqn:cgcoeffdef} and \bsrefeqn{eqn:spintensorvshcoeffsdef} respectively.
\end{lemma}

@@

\bstodoinline{Do the derivation of these rec coeffs, to have as the proof (and check they are correct!)}

>>>>

\chapter{Spherical harmonics as orthogonal polynomials}

@@

\begin{lemma}
	For $l \in \No$, $m \in \Z$ s.t. $0 \le |m| \le l$, the spherical harmonics satisfy the relationships:
\bseqnnumber{
	x\,\Ylm(x,y,z) &= \alpha_{l,m,1} Y^{m-1}_{l-1}(x,y,z) +  \alpha_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \nonumber \\
		     & \quad \quad \quad + \alpha_{l,m,3} Y^{m-1}_{l+1}(x,y,z) + \alpha_{l,m,4} Y^{m+1}_{l+1}(x,y,z), \label{eqn:shrecx} \\
	y\,\Ylm(x,y,z) &= \beta_{l,m,1} Y^{m-1}_{l-1}(x,y,z) +  \beta_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \nonumber \\
		     & \quad \quad \quad + \beta_{l,m,3} Y^{m-1}_{l+1}(x,y,z) + \beta_{l,m,4} Y^{m+1}_{l+1}(x,y,z), \label{eqn:shrecy} \\
	z\,\Ylm(x,y,z) &= \gamma_{l,m,1} Y^{m}_{l-1}(x,y,z) + \gamma_{l,m,2} Y^{m}_{l+1}(x,y,z), \label{eqn:shrecz}
}
where
\bseqn{
	\alpha_{l,m,1} &:= 
		\begin{cases}
			\frac{\clm}{2c^{m-1}_{l-1}} \tilde \alpha_{l,m,1} \quad \text{if } m>0 \\
			\frac{\clm}{2c^{m-1}_{l-1}} \tilde \alpha_{l,|m|,2} \quad \text{if } m\le0 , \, l - |m| \ge 2 \\
			\quad \quad 0 \quad \quad \quad \quad \text{otherwise} 
		\end{cases} \\ 
	\alpha_{l,m,2} &:= 
		\begin{cases}
			\frac{\clm}{2c^{m+1}_{l-1}} \tilde \alpha_{l,m,2} \quad \text{if } m\ge0, \, l - |m| \ge 2 \\
			\frac{\clm}{2c^{m+1}_{l-1}} \tilde \alpha_{l,|m|,1} \quad \text{if } m<0 \\
			\quad \quad 0 \quad \quad \quad \quad \text{otherwise} 
		\end{cases} \\
	\alpha_{l,m,3} &:= 
		\begin{cases}
			\frac{\clm}{2c^{m-1}_{l+1}} \tilde \alpha_{l,m,3} \quad \text{if } m>0 \\
			\frac{\clm}{2c^{m-1}_{l+1}} \tilde \alpha_{l,|m|,4} \quad \text{if } m\le0 
		\end{cases} \\
	\alpha_{l,m,4} &:=
		\begin{cases}
			\frac{\clm}{2c^{m+1}_{l+1}} \tilde \alpha_{l,m,4} \quad \text{if } m\ge0 \\
			\frac{\clm}{2c^{m+1}_{l+1}} \tilde \alpha_{l,|m|,3} \quad \text{if } m<0 
		\end{cases} \\
	\beta_{l,m,j} &:= (-1)^{j+1} \: i \: \alpha_{l,m,j}, \quad j = 1,2,3,4 \\
	\gamma_{l,m,1} &:= \frac{\clm}{c^{m}_{l-1}} \: \tilde \gamma_{l,m,1} \\
	\gamma_{l,m,2} &:= \frac{\clm}{c^{m}_{l+1}} \: \tilde \gamma_{l,m,2}.
}
and
\bseqn{
	\tilde \alpha_{l,m,1} &:= \frac{2l}{2l+1} \\
	\tilde \alpha_{l,m,2} &:= 
		\begin{cases}
			- \frac{l}{2(2l+1)} \quad \text{if } l - m \ge 2 \\
			\quad \quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \alpha_{l,m,3} &:= - \frac{2(l-m+2)(l-m+1)}{(2l+1)(l+1)} \\
	\tilde \alpha_{l,m,4} &:= \frac{(l+m+2)(l+m+1)}{2(2l+1)(l+1)} \\
	\tilde \gamma_{l,m,1} &:= \begin{cases}
			\frac{l}{2l+1} \quad \text{if } l - m \ge 1 \\
			\quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \gamma_{l,m,2} &:= \frac{(l-m+1)(l+m+1)}{(2l+1)(l+1)}.
}
\end{lemma}

@@

\subsection{Obtaining operator matrices for variable coefficients}

@@

%%%
\section{Vector spherical harmonics as orthogonal vectors in three variables}

@@

\subsection{Jacobi matrices} %{Spin-1 tensor spherical harmonics}

\bstodoinline{cite C-G coeffs, spin-1 tensor harmonics, and the combination expression in \label{eqn:VSHsalt}}
\bstodoinline{get better reference than that Winter 2017 physics document}

We start as before for the scalar case by finding $x \,\gradYlm (x,y,z)$, $x \,\gradpYlm (x,y,z)$ etc. in terms of $\gradY^{m'}_{l'} (x,y,z)$, $\gradpY^{m'}_{l'} (x,y,z)$. To this end, we use the helpful property that the vector spherical harmonics as defined in \bsrefeqn{eqn:VSHs} can be expressed in terms of \textit{spin-1 tensor spherical harmonics}, which in turn can each be expressed as a vector-weighted sum of spherical harmonics \cite{khersonskii1988quantum}.

We start by defining what we mean by a spin-1 tensor spherical harmonic. In general, the tensor spherical harmonic is given by, for $2l, \, j, \, 2s \in \No$, \cite{}
\bseqn{
	\curlyy^{j,s}_{l,m}(x,y,z) = \sum_{m_s=-s}^s \langle j \quad m-m_s \; ; \; s \quad m_s \; | \; l \quad m \rangle \, Y^{m-m_s}_j (x,y,z) \, \vec{\chi}_{s, m_s},
}
where $\vec{\chi}_{s, m_s}$ are the simultaneous eigenstates of the spin operators $\bold{S}^2$ and $S_z$, and where $\langle j \quad m-m_s \; ; \; s \quad m_s \; | \; l \quad m \rangle$ is a Clebsch--Gordan coefficient \cite{} . We note that a property of the Clebsch--Gordan coefficients means that they vanish unless $|j - s| \le l \le j + s$ \cite{}. We further note that there are simple calculable expressions for the Clebsch--Gordan coefficients when the spin $s=1$ \cite{}.

To simplify the notation, for spin $s=1$, we define
\bseqnnumber{
	\cgcoeff^{L, m_s}_{l, m} := \, \langle L \quad m-m_s \; ; \; 1 \quad m_s \; | \; l \quad m \rangle. \label{eqn:cgcoeffdef}
}
Thus we have that the three spin-1 tensor spherical harmonics are given by
\bseqn{
	\curlyy^{l \pm1,1}_{l,m}(x,y,z) &= \sum_{m_s=-1}^1 \cgcoeff^{l\pm1, m_s}_{l, m} \, Y^{m-m_s}_{l \pm 1} (x,y,z) \, \chivec, \\
	\curlyy^{l,1}_{l,m}(x,y,z) &= \sum_{m_s=-1}^1 \cgcoeff^{l, m_s}_{l, m} \, Y^{m-m_s}_l (x,y,z) \, \chivec.
}

Here, the vectors $\chivec$ are the orthonormal eigenvectors of the matrix
\bseqn{
	S_3 = \begin{pmatrix} 0 & -i & 0 \\ i & 0 & 0 \\ 0 & 0 & 0 \end{pmatrix},
}
and so are given as
\bseqn{
	\vec{\chi}_{1, \pm 1} = \frac{1}{\sqrt{2}} \begin{pmatrix} \mp 1 \\ -i \\ 0 \end{pmatrix}, \quad \vec{\chi}_{1,0} = \begin{pmatrix} 0 \\ 0 \\ 1 \end{pmatrix}.
}
Then, for any $l \in \No$, $m \in \Z$ s.t. $0 \le |m| \le l$ we have that
\bseqnnumber{
	\gradYlm &= \mu_{l,-1} \, \curlyy^{l-1,1}_{l,m} + \mu_{l,1} \curlyy^{l+1,1}_{l,m}, \quad \gradpYlm = \mu_{l,0} \, \curlyy^{l,1}_{l,m}, \label{eqn:VSHsalt}
}
where
\bseqnnumber{
	\mu_{l,-1} &:= (l+1) \, \Big(\frac{l}{2l+1}\Big)^\half, \quad
	\mu_{l,0} := i \, \big(l(l+1)\big)^\half, \quad 
	\mu_{l,1} := l \, \Big(\frac{l+1}{2l+1}\Big)^\half. \label{eqn:spintensorvshcoeffsdef}
}

The expressions for the VSHs as given in \bsrefeqn{eqn:VSHsalt} allow us to be able to find the coefficients for our desired expressions for $x \gradYlm$, $y \gradYlm$ and $z \gradYlm$. 
\begin{lemma}\label{lemma:VSHrecurrences}
	For $l \in \No$, $-l \le m \le l$ the vector spherical harmonics satisfy the relationships:
	x \gradYlm &= A_{l,m,1} \gradY^{m-1}_{l-1} + A_{l,m,2} \gradY^{m+1}_{l-1} + A_{l,m,3} \gradY^{m-1}_{l+1} + A_{l,m,4} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + A_{l,m,5} \gradpY^{m-1}_{l} + A_{l,m,6} \gradpY^{m+1}_{l}, \\
	x \gradpYlm &= A_{l,m,1} \gradpY^{m-1}_{l-1} + A_{l,m,2} \gradpY^{m+1}_{l-1} + A_{l,m,3} \gradpY^{m-1}_{l+1} + A_{l,m,4} \gradpY^{m+1}_{l+1} \\
& \quad \quad \quad - A_{l,m,5} \gradY^{m-1}_{l} - A_{l,m,6} \gradY^{m+1}_{l}, \\
	y \gradYlm &= B_{l,m,1} \gradY^{m-1}_{l-1} + B_{l,m,2} \gradY^{m+1}_{l-1} + B_{l,m,3} \gradY^{m-1}_{l+1} + B_{l,m,4} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + B_{l,m,5} \gradpY^{m-1}_{l} + B_{l,m,6} \gradpY^{m+1}_{l}, \\
	y \gradpYlm &= B_{l,m,1} \gradpY^{m-1}_{l-1} + B_{l,m,2} \gradpY^{m+1}_{l-1} + B_{l,m,3} \gradpY^{m-1}_{l+1} + B_{l,m,4} \gradpY^{m+1}_{l+1} \\
& \quad \quad \quad - B_{l,m,5} \gradY^{m-1}_{l} - B_{l,m,6} \gradY^{m+1}_{l}, \\
	z \gradYlm &= \Gamma_{l,m,1} \gradY^{m}_{l-1} + \Gamma_{l,m,2} \gradY^{m}_{l+1} + \Gamma_{l,m,3} \gradpY^{m}_{l}, \\
	z \gradpYlm &= \Gamma_{l,m,1} \gradpY^{m}_{l-1} + \Gamma_{l,m,2} \gradpY^{m}_{l+1} - \Gamma_{l,m,3} \gradY^{m}_{l}
%\bseqn{
%	x \gradYlm &= A_{l,m,1} \gradY^{m-1}_{l-1} + A_{l,m,2} \gradY^{m+1}_{l-1} + A_{l,m,5} \gradY^{m-1}_{l+1} + A_{l,m,6} \gradY^{m+1}_{l+1} \\
%& \quad \quad \quad + A_{l,m,3}^{*} \gradpY^{m-1}_{l} + A_{l,m,4}^{*} \gradpY^{m+1}_{l}, \\
%	x \gradpYlm &= A_{l,m,1}^{*} \gradpY^{m-1}_{l-1} + A_{l,m,2}^{*} \gradpY^{m+1}_{l-1} + A_{l,m,5}^{*} \gradpY^{m-1}_{l+1} + A_{l,m,6}^{*} \gradpY^{m+1}_{l+1} \\
%	& \quad \quad \quad + A_{l,m,3} \gradY^{m+1}_{l} + A_{l,m,4} \gradY^{m-1}_{l}, \\
%	y \gradYlm &= B_{l,m,1} \gradY^{m-1}_{l-1} + B_{l,m,2} \gradY^{m+1}_{l-1} + B_{l,m,5} \gradY^{m-1}_{l+1} + B_{l,m,6} \gradY^{m+1}_{l+1} \\
%& \quad \quad \quad + B_{l,m,3}^{*} \gradpY^{m-1}_{l} + B_{l,m,4}^{*} \gradpY^{m+1}_{l}, \\
%	y \gradpYlm &= B_{l,m,1}^{*} \gradpY^{m-1}_{l-1} + B_{l,m,2}^{*} \gradpY^{m+1}_{l-1} + B_{l,m,5}^{*} \gradpY^{m-1}_{l+1} + B_{l,m,6}^{*} \gradpY^{m+1}_{l+1} \\
%	& \quad \quad \quad + B_{l,m,3} \gradY^{m+1}_{l} + B_{l,m,4} \gradY^{m-1}_{l}, \\
%	z \gradYlm &= \Gamma_{l,m,1} \gradY^{m}_{l-1} + \Gamma_{l,m,3} \gradY^{m}_{l+1} + \Gamma_{l,m,2}^* \gradpY^{m}_{l}, \\
%	z \gradpYlm &= \Gamma_{l,m,1}^* \gradpY^{m}_{l-1} + \Gamma_{l,m,3}^* \gradpY^{m}_{l+1} + \Gamma_{l,m,2} \gradY^{m}_{l}
%}
%where $*$ denotes the complex conjugate, and where, for any valid $m_s$ value,
where, for any valid $m_s$ value,
	A_{l,m,1} &:= \frac{\mu_{l,-1}}{\mu_{l-1,-1}} \frac{\cgcoeff^{l-1,m_s}_{l,m}}{\cgcoeff^{l-2,m_s}_{l-1,m-1}} \alpha_{l-1,m-m_s,1}, \\
	A_{l,m,2} &:= \frac{\mu_{l,-1}}{\mu_{l-1,-1}} \frac{\cgcoeff^{l-1,m_s}_{l,m}}{\cgcoeff^{l-2,m_s}_{l-1,m+1}} \alpha_{l-1,m-m_s,2}, \\
	A_{l,m,3} &:= \frac{\mu_{l,1}}{\mu_{l+1,1}} \frac{\cgcoeff^{l+1,m_s}_{l,m}}{\cgcoeff^{l+2,m_s}_{l+1,m-1}} \alpha_{l+1,m-m_s,3}, \\
	A_{l,m,4} &:= \frac{\mu_{l,1}}{\mu_{l+1,1}} \frac{\cgcoeff^{l+1,m_s}_{l,m}}{\cgcoeff^{l+2,m_s}_{l+1,m+1}} \alpha_{l+1,m-m_s,4}, \\
	A_{l,m,5} &:= \frac{1}{\mu_{l,0} \, \cgcoeff^{l,m_s}_{l, m-1}} \, \Big[ \cgcoeff^{l-1,m_s}_{l,m} \, \mu_{l,-1} \, \alpha_{l-1,m-m_s,3} + \cgcoeff^{l+1,m_s}_{l,m} \, \mu_{l,1} \, \alpha_{l-1,m-m_s,1} \\
	& \quad \quad \quad \quad \quad \quad \quad - A_{l,m,3} \, \mu_{l+1,-1} \, \cgcoeff^{l,m_s}_{l+1,m-1} - A_{l,m,1} \, \mu_{l-1,1} \, \cgcoeff^{l,m_s}_{l-1,m-1} \Big], \\	
	A_{l,m,6} &:= \frac{1}{\mu_{l,0} \, \cgcoeff^{l,m_s}_{l, m+1}} \, \Big[ \cgcoeff^{l-1,m_s}_{l,m} \, \mu_{l,-1} \, \alpha_{l-1,m-m_s,4} + \cgcoeff^{l+1,m_s}_{l,m} \, \mu_{l,1} \, \alpha_{l-1,m-m_s,2} \\
	& \quad \quad \quad \quad \quad \quad \quad - A_{l,m,4} \, \mu_{l+1,-1} \, \cgcoeff^{l,m_s}_{l+1,m+1} - A_{l,m,2} \, \mu_{l-1,1} \, \cgcoeff^{l,m_s}_{l-1,m+1} \Big], \\
	B_{l,m,j} &:= i (-1)^{j+1} A_{l,m,j} \quad \text{for } j = 1,\dots,6, \\
	\Gamma_{l,m,1} &:= \frac{\mu_{l,-1}}{\mu_{l-1,-1}} \frac{\cgcoeff^{l-1,m_s}_{l,m}}{\cgcoeff^{l-2,m_s}_{l-1,m}} \gamma_{l-1,m-m_s,1}, \\
	\Gamma_{l,m,2} &:= \frac{\mu_{l,1}}{\mu_{l+1,1}} \frac{\cgcoeff^{l+1,m_s}_{l,m}}{\cgcoeff^{l+2,m_s}_{l+1,m}} \gamma_{l+1,m-m_s,2}, \\
	\Gamma_{l,m,3} &:= \frac{1}{\mu_{l,0} \, \cgcoeff^{l,m_s}_{l, m}} \, \Big[ \cgcoeff^{l-1,m_s}_{l,m} \, \mu_{l,-1} \, \gamma_{l-1,m-m_s,2} + \cgcoeff^{l+1,m_s}_{l,m} \, \mu_{l,1} \, \gamma_{l+1,m-m_s,1} \\
	& \quad \quad \quad \quad \quad \quad \quad - \Gamma_{l,m,3} \, \mu_{l+1,-1} \, \cgcoeff^{l,m_s}_{l+1,m} - \Gamma_{l,m,1} \, \mu_{l-1,1} \, \cgcoeff^{l,m_s}_{l-1,1} \Big],
and where $\cgcoeff^{L,m_s}_{l,m}$, $\mu_{l,k}$ are defined in \bsrefeqn{eqn:cgcoeffdef} and \bsrefeqn{eqn:spintensorvshcoeffsdef} respectively.
\end{lemma}

@@

\bstodoinline{Do the derivation of these rec coeffs, to have as the proof (and check they are correct!). Need to account for l=1 case.}
